Development of Physics or HPC Optimisation of a parallel 2D lattice Boltzmann solver using GPUs/CUDA

### 2017-08-12 Thesis/Draft.tex
fix small things

\subsection{Rayleigh-Taylor instability}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{Resources/Images/rt.png}
	\caption{Blue fluid density for the 2D Rayleigh-Taylor instability}
	\label{fig:rt}
\end{figure}
In this test, a bubble following an ellipsoid is created inside another fluid. The bubble then starts oscillating vertically and horizontally until it stabilizes into a steady bubble. The needs for this case are similar to the oscillating bubble case, but instead of calculating the maximum height of the interface we calculate the minimum. Because of the same memory access and number of computations, this is the third most computationally expensive test in the new LBM solver.

>>>>

\subsection{Rayleigh-Taylor instability}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{Resources/Images/rt.png}
	\caption{Blue fluid density for the 2D Rayleigh-Taylor instability}
	\label{fig:rt}
\end{figure}
Finally, we chose to implement the Rayleigh-Taylor instability since in this test we can adequately test the functionalities of our CG model. Here, a heavy fluid is set on top of another, lighter fluid. Then the heavier fluid starts descending with the force of gravity and eventually starts creating vortices in the other fluid. The needs for this case are similar to the oscillating bubble case, but instead of calculating the maximum height of the interface we calculate the minimum. Because of the same memory access and number of computations, this is the third most computationally expensive test in the new LBM solver.
